Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow} ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex} ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}

### 2015-10-23 latex/article.tex
minor edit

Then, we compare the approximation made by computing curvature from level $l >=
l_0$ in Figure~\ref{fig:refine}. We can see that results using approximation
seems to fastly converge to the ground truth results.
Table~\ref{tab:full-res-stat} shows numerical results of $L_\infty$ error (worst
case) and $L_2$ error (mean), as well the number of \emph{mipmap texture}
fetches. We can first see that the number of texel fetch required to compute the
curvature reduces drastically when computing the approximations. This is
mandatory if we want to increase the framerate.

@@

\begin{table}
  \begin{center}

	\begin{tabular}{@{}lrrrrr@{}}
      \toprule
      & \multicolumn{5}{c}{$R=8$}\\
      \cmidrule(r){2-6}
    Quantities & ~~~H & $l_3$ & $l_2$ & $l_1$ & $l_0$\\
      \midrule
      Number of texture fetches &
      1468 & 2 & 28 & 260 & 2104\\
      %Time (in ms) &
      %208 & 15 & 26 & 93 & 642\\
      $L_\infty$ error (\wrt $l_0$) &
      0.051 & 0.306 & 0.085 & 0.047 & 0\\
      $L_2$ error (\wrt $l_0$) &
      3.51e-05 & 2.67e-04 & 7.57e-05 & 2.02e-05 & 0\\
      \bottomrule
    \end{tabular}
	\begin{tabular}{@{}lrrrrrr@{}}
      \toprule
      & \multicolumn{6}{c}{$R=16$}\\
      \cmidrule(r){2-7}
    Quantities & ~~~H & $l_4$ & $l_3$ & $l_2$ & $l_1$ & $l_0$\\
      \midrule
      Number of texture fetches &
      5706 & 2 & 28 & 90 & 2120 & 17080\\
      %Time (in ms) &
      %826 & 14 & 26 & 252 & 606 & 4801\\
      $L_\infty$ error (\wrt $l_0$) &
      0.053 & 0.146 & 0.041 & 0.017 & 0.005 & 0\\
      $L_2$ error (\wrt $l_0$) &
      4.43e-05 & 1.39e-04 & 4.16e-05 & 1.57e-05 & 2.07e-06 & 0\\
      \bottomrule
    \end{tabular}
  \end{center}
  %
  \caption{Comparison of number of texture fetches, $L_2$ and $L_\infty$ error
  obtained on OctaFlower with a digital domain of $130^3$ when computing mean
  curvature, with two radii: 8 and 16. The object is triangulated at full
  resolution with a regular grid and contains 282,396 vertices.
  %
  \label{tab:full-res-stat}}
  %
\end{table}

>>>>

Then, we compare the approximation made by computing curvature from level $l \ge
l_0$ in Figure~\ref{fig:refine}. We can see that results using approximation
seems to fastly converge to the ground truth results.
Table~\ref{tab:full-res-stat} shows numerical results of $L_\infty$ error (worst
case) and $L_2$ error (mean), as well the number of \emph{mipmap texture}
fetches. We can first see that the number of texel fetch required to compute the
curvature reduces drastically when computing the approximations. This is
mandatory if we want to increase the framerate.

@@

\begin{table}
  \begin{center}
  \setlength{\tabcolsep}{0.15cm}
	\begin{tabular}{@{}llrrrrrr@{}}
      \toprule
        & & H & $l_4$ & $l_3$ & $l_2$ & $l_1$ & $l_0$\\
      \midrule
      \multirow{2}{2.2cm}{Number of texture fetches} & $R=8$ & 1468 & & 2 & 28 & 260 & 2104 \\
                                & $R=16$ & 5706 & 2 & 28 & 90 & 2120 & 17080\\\midrule

      \multirow{2}{2.2cm}{$L_\infty$ error (\wrt $l_0$)} & $R=8$ & 0.051 & & 0.306 & 0.085 & 0.047 & 0\\
                                    & $R=16$ & 0.053 & 0.146 & 0.041 & 0.017 & 0.005 & 0\\\midrule

      \multirow{2}{2.1cm}{$L_2$ error (\wrt $l_0$)} & $R=8$ & 3.51e-05 & & 2.67e-04 & 7.57e-05 & 2.02e-05 & 0\\
                               & $R=16$ & 4.43e-05 & 1.39e-04 & 4.16e-05 & 1.57e-05 & 2.07e-06 & 0\\
      \bottomrule
    \end{tabular}
  \end{center}
  %
  \caption{Comparison of number of texture fetches, $L_2$ and $L_\infty$ error
  obtained on OctaFlower with a digital domain of $130^3$ when computing mean
  curvature with two radii: 8 and 16, with hierarchical algorithm (H) and $l \ge
  l_0$ approximation algorithms. The object is triangulated at full resolution
  with a regular grid and contains 282,396 vertices.
  %
  \label{tab:full-res-stat}}
  %
\end{table}
